On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-09-26 paper.tex
Added definition of Steinberg groups

\subsection{Steinberg groups and relative Steinberg groups}
\subsection{Relative Steinberg groups}

\[ T_{ij}(at^{-1}) = \sigma_i T_{ij}(a) \sigma_i^{-1} = \sigma_j^{-1} T_{ij}(a) \sigma_j \]
\[ [[x_{ij}(a t^{-1}), x_{jk}(b t^{-1})],  x_{kl}(c)] = [x_{ik}(a b t^{-1}),  x_{kl}(c t^{-1})] \]
\[ \sigma_i [[x_{ij}(a), x_{jk}(b t^{-1})],  x_{kl}(c)] \sigma_i^{-1} =  \sigma_i [x_{ik}(a b),  x_{kl}(c t^{-1})] \sigma_i^{-1} \]
\begin{multline}
[[x_{ij}(at^{-1}), x_{jk}(bt^{-1})], x_{jl}(ct^{-1})] = \sigma_i [[ x_{ij}(a), x_{jk}(bt^{-1})], x_{jl}(ct^{-1})] \sigma_i^{-1} = \\
\sigma_i \sigma_k^{-1} \sigma_l^{-1} [[ x_{ij}(a), x_{jk}(b)], x_{jl}(c)] \sigma_l \sigma_k \sigma_i^{-1} = 1
\end{multline}
\[ [b, c] =1,\ [a^c, b] = c^{-1} a c b c^{-1} a^{-1} c b^{-1} =  c^{-1} a b  a^{-1} b^{-1} c = [a, b]^c \]

>>>>

\subsection{Steinberg groups}
Let $\Phi$ be a reduced and irreducible root system of rank $\geq 2$ and $R$ be a commutative ring with $1$.
Recall that the \emph{Steinberg group} $\St(\Phi, R)$ is defined by means of generators
$\mathcal{X}_{\Phi, R} = \{x_{\alpha}(\xi) \mid \xi\in R, \alpha\in\Phi\}$ and the set of relations $\mathcal{R}_{\Phi, R}$ 
consisting of the following two families of relations:
\begin{align}
& \phantom{[}
x_\alpha(s) x_\alpha(t) = x_\alpha(s+t),\ \alpha\in\Phi,\ s,t\in R; \label{rel:add}\\
& [x_\alpha(s), x_\beta(t)] = \prod\limits_{i,j\in\mathbb{N}}
 x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha,\beta\in\Phi,\ \alpha\neq\pm\beta,\ s,t\in R. \label{rel:CCF}
\end{align}
The indices $i$, $j$ appearing in the right-hand side of the above relation range over
all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
%The structure constants $N_{\alpha \beta i j}=\pm 1,2,3$ appearing in \eqref{rel:CCF} depend only on $\Phi$ and can be computed precisely.

It is clear the above construction is functorial in $R$ and so there is a functor $\St(\Phi, -)\colon \catname{CRings}\to \catname{Groups}$.
\subsection{Relative Steinberg groups}
First of all, let us recall the definition of the category of pairs. 
As suggested by the notation, the objects of $\catname{Pairs}$ are pairs $(R, I)$ consisting of a unital commutative ring $R$ and an ideal $I \trianglelefteq R$.
The set of morphisms between $(R, I)$ and $(S, J)$ is defined as the set of all ring-theoretic maps $f\colon R\to S$ such that $f(I)\subseteq J$.
There is an obvious fully faithful embedding $\iota\colon \catname{CRings} \to \catname{Pairs}$ defined on objects by $\iota(R) = (R, R)$.
Now if there is a functor $F\colon \catname{CRings}\to \catname{Grp}$ then its {\it relativization} is another functor $\widetilde{F}\colon \catname{Pairs} \to \catname{Groups}$
such that $\widetilde{F} \iota = F$.

Recall that there is a way to ``relativize`` the Steinberg group functor, that is define a group-valued functor $\St(\Phi, -)$ on the category of pairs
 in a way compatible with the embedding

\begin{equation}
 \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r] & \St(\Phi, R) \ar[r] & \St(\Phi, R/I) \ar[r] & 1 }
\end{equation}

\subsection{Various stuff}
\[ T_{ij}(at^{-1}) = \sigma_i T_{ij}(a) \sigma_i^{-1} = \sigma_j^{-1} T_{ij}(a) \sigma_j \]
\[ [[x_{ij}(a t^{-1}), x_{jk}(b t^{-1})],  x_{kl}(c)] = [x_{ik}(a b t^{-1}),  x_{kl}(c t^{-1})] \]
\[ \sigma_i [[x_{ij}(a), x_{jk}(b t^{-1})],  x_{kl}(c)] \sigma_i^{-1} =  \sigma_i [x_{ik}(a b),  x_{kl}(c t^{-1})] \sigma_i^{-1} \]
\begin{multline}
[[x_{ij}(at^{-1}), x_{jk}(bt^{-1})], x_{jl}(ct^{-1})] = \sigma_i [[ x_{ij}(a), x_{jk}(bt^{-1})], x_{jl}(ct^{-1})] \sigma_i^{-1} = \\
\sigma_i \sigma_k^{-1} \sigma_l^{-1} [[ x_{ij}(a), x_{jk}(b)], x_{jl}(c)] \sigma_l \sigma_k \sigma_i^{-1} = 1
\end{multline}
\[ [b, c] =1,\ [a^c, b] = c^{-1} a c b c^{-1} a^{-1} c b^{-1} =  c^{-1} a b  a^{-1} b^{-1} c = [a, b]^c \]
